---
name: Gabriel-Mateus
surname: Bernardo Harrington
position: "Research Associate"
address: "School of Medicine, Dementia Research Institue"
#phone: +44 077 777 77777
profilepic: avatar.jpeg
www: gmbernardoharrington.netlify.app
#twitter: Hmateus4
github: H-Mateus
linkedin: gmb-harrington
orcid: 0000-0001-6075-3619
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Experienced and motivated scientist with a strong publication track record. My multidisciplinary skills in both informatics and bench work gives me a unique perspective and has made me highly adaptable."
#output: vitae::twentyseconds
#headcolor: 009ACD
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

## load packages, xfun will install packages if they aren't installed already
require(xfun)

packages <- c("vitae",
              "tibble",
              "rorcid",
              "readr",
              "dplyr",
              "lubridate",
              "glue",
              "here"
)

xfun::pkg_attach2(packages, message = FALSE)

## read in data
df <- read_csv(here("cv_basis/awarded_funding.csv")) %>%
  dplyr::mutate(start_year = lubridate::year(start), 
                end_year = lubridate::year(end))
```

```{r}
skills <- tribble(
    ~area, ~skills,
    "Bioinformatics", "Proteomics, Genomics, High performance cluster computing, SLURM, Electronic Health data",
    "Programming Languages", "R, BASH, Python, SQL, Nextflow",
    "Wet Lab work", "3D Tissue Culture, Microscopy, Animal handling, Histology",
    "Markup Languages", "Markdown, RMarkdown/Quarto, YAML, CSS, HTML, LaTeX",
    "Version Control", "Git, GitHub, GitLab",
    "Language", "Portuguese",
    "Microsoft Office", "Excel, Outlook, OneNote, PowerPoint, Word"
)
```

```{r load-orcid-data}
## education data
orcid_education_data <- do.call("rbind",
  rorcid::orcid_educations("0000-0001-6075-3619")$`0000-0001-6075-3619`$`affiliation-group`$summaries
)
## awards data
orcid_distinctions_data <- do.call("rbind",
  rorcid::orcid_distinctions("0000-0001-6075-3619")$`0000-0001-6075-3619`$`affiliation-group`$summaries
)
## funding data
orcid_funding_data <- do.call("rbind",
  rorcid::orcid_fundings("0000-0001-6075-3619")$`0000-0001-6075-3619`$group$`funding-summary`
)
```

# Professional Overview

Experienced bioinformtician with a strong track record in the field of spinal cord injury and Alzheimer's disease.
Extremely adaptable with a highly interdisciplinary background of bench work, proteomics, genomics and bioinformatics.
Accomplished in working with diverse teams, including clinical and patient-facing settings.
My leadership with informatic colleagues in working more cohesively and reproducibly by promoting the use of version control, containerisation and continuous integrations has streamlined our projects, reduced errors and improved quality.
Related experience in training colleagues in the use of tools such as Git, GitHub/GitLab, R Markdown/Quarto and Docker.

# Education

```{r}
orcid_education_data %>%
  detailed_entries(
    what = `education-summary.role-title`,
    when = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
    with = `education-summary.organization.name`,
    where = `education-summary.organization.address.city`
  )
```

# Awards

```{r}
#tribble(
#  ~Year, ~Type, ~Desc,
#  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
#  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
#) %>% 
#  brief_entries(
#    glue::glue("Nobel Prize in {Type}"),
#    Year, 
#    Desc
#  )
```

```{r}
orcid_distinctions_data %>%
  detailed_entries(
    what = glue::glue("{`distinction-summary.department-name`} - {`distinction-summary.role-title`}"),
    when = `distinction-summary.start-date.year.value`,
    with = `distinction-summary.organization.name`,
    where = `distinction-summary.organization.address.city`
  )
```

# Funding

```{r}
df %>% 
  dplyr::filter(type == "funding") %>%
  detailed_entries(
    what = what,
    when = glue::glue("{start_year}"),
    with = with,
    where = city,
    why = glue::glue("£{amount} awarded")
  )
```

# Talks

```{r}
df %>%
  dplyr::filter(type == "talk") %>%
  detailed_entries(
    what = what,
    when = start_year,
    with = with,
    where = city
  ) %>%
  dplyr::arrange(desc(when))
```

# Skills

```{r skills}
skills %>%
  detailed_entries(
    with = area,
    what = skills
  )
```

# Publications

```{r}
library(dplyr)
#knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries(here("cv_basis/publications.bib")) %>%
  arrange(author$family, issued)
```
