---
name: Gabriel-Mateus
surname: Bernardo Harrington
position: "Research Associate"
address: "School of Medicine, Dementia Research Institue"
#phone: +44 077 390 47519
profilepic: avatar.png
www: gmbernardoharrington.netlify.app
email: "Bernardo-HarringtonG@cardiff.ac.uk"
#twitter: Hmateus4
github: H-Mateus
linkedin: gmb-harrington
orcid: 0000-0001-6075-3619
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Currently a Research Associate as a bioinformatician at the Dementia Research Institute, Cardiff University, working on Alzheimer's disease with a focus towards genomics."
output: vitae::twentyseconds
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

## load packages, xfun will install packages if they aren't installed already
require(xfun)

packages <- c("vitae",
              "tibble",
              "rorcid",
              "readr",
              "dplyr",
              "lubridate",
              "glue",
              "here"
)

xfun::pkg_attach2(packages, message = FALSE)

## read in data
df <- read_csv("awarded_funding.csv") %>%
  dplyr::mutate(start_year = lubridate::year(start), 
                end_year = lubridate::year(end))
```

```{r load-orcid-data}
## education data
orcid_education_data <- do.call("rbind",
  rorcid::orcid_educations("0000-0001-6075-3619")$`0000-0001-6075-3619`$`affiliation-group`$summaries
)
## awards data
orcid_distinctions_data <- do.call("rbind",
  rorcid::orcid_distinctions("0000-0001-6075-3619")$`0000-0001-6075-3619`$`affiliation-group`$summaries
)
## funding data
orcid_funding_data <- do.call("rbind",
  rorcid::orcid_fundings("0000-0001-6075-3619")$`0000-0001-6075-3619`$group$`funding-summary`
)
```

# Research profile

Currently a Research Associate Alzheimer's Disease group within the [Dementia Research Institute](https://ukdri.ac.uk/) at [Cardiff University](https://www.cardiff.ac.uk/) as a bioinformatician.

My PhD at Keele University based in the [OsKOR](https://oskor.netlify.app/) group at The [RJAH Orthopaedic Hospital](https://www.rjah.nhs.uk/) focused on spinal cord injury (SCI).
SCI is damage to the spinal cord due to trauma, degeneration or disease that results in a temporary/permanent change to neurological function, recovery from which is highly variable, stymieing development of novel therapies as powering clinical trials is extremely difficult.
SCI can lead to devastating consequences for both the physical and mental health of patients, particularly due to the uncertainty of neurological outcomes in the first two weeks post-injury.

I endeavour to discover novel biomarkers of SCI outcomes, both to minimise this uncertainty and to expand our understanding of the underlying pathology of neurological recovery.
I use a combination of modelling patient data and proteomic techniques to this end, and have identified a relationship between markers of liver health and SCI recovery.

The lab rotations in the first year of my PhD also allowed me to greatly develop my skills at the bench.
At Loughborough University, I investigated genetic expression in hydrogels, gaining experience in 3D tissue culture, hydrogels and PCR.
At Nottingham University I studied the effects of alternating current on interfacing wires grown via wireless electrochemistry and gained experience in 3D printing, electrodeposition and microscopy.
At Keele University I cultured multiple cell types in 3D and compared viability and growth kinetics via cell staining, fluorescent microscopy.
These experiences have given me a highly cross-disciplinary skillset making me a flexible and versatile scientist.

# Education

```{r}
orcid_education_data %>%
  detailed_entries(
    what = `education-summary.role-title`,
    when = glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
    with = `education-summary.organization.name`,
    where = `education-summary.organization.address.city`
  )
```

# Awards

```{r}
#tribble(
#  ~Year, ~Type, ~Desc,
#  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
#  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
#) %>% 
#  brief_entries(
#    glue::glue("Nobel Prize in {Type}"),
#    Year, 
#    Desc
#  )
```

```{r}
orcid_distinctions_data %>%
  detailed_entries(
    what = glue::glue("{`distinction-summary.department-name`} - {`distinction-summary.role-title`}"),
    when = `distinction-summary.start-date.year.value`,
    with = `distinction-summary.organization.name`,
    where = `distinction-summary.organization.address.city`
  )
```

# Funding

```{r}
df %>% 
  dplyr::filter(type == "funding") %>%
  detailed_entries(
    what = what,
    when = glue::glue("{start_year} - {end_year}"),
    with = with,
    where = city,
    why = glue::glue("£{amount} awarded")
  )
```

# Talks

```{r}
df %>%
  dplyr::filter(type == "talk") %>%
  detailed_entries(
    what = what,
    when = start_year,
    with = with,
    where = city
  )
```

# Skills

```{r skills}
df %>% 
  dplyr::filter(type == "skill") %>%
  detailed_entries(
    what = what,
    with = with
  )
```

# Publications

```{r}
library(dplyr)
#knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("publications.bib") %>%
  arrange(desc(author$family), issued)
```
